---
title: "Response CI"
author: "XiangningXue"
date: "5/19/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
  bibliography: ResponsCI.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
r.2by2 = function(n1, n0, S, C){
  x11 = rbinom(1, n1, S)
  x00 = rbinom(1, n0, C)
  tab.2by2 = cbind.data.frame(c(x11, n1-x11), c(n0-x00, x00))
  colnames(tab.2by2) = c("Disease1", "Disease0")
  rownames(tab.2by2) = c("Test1", "Test0")
  return(tab.2by2)
}
# get.PPV.NPC = function(tab, p, alpha = 0.05){
#   k = qnorm(1-alpha/2)
#   n1.tilda = tab[1, 1]+tab[2, 1] + k^2
#   n0.tilda = tab[1, 2]+tab[2, 2] + k^2
#   S.tilda = (tab[1, 1]+k^2/2)/n1.tilda
#   C.tilda = (tab[2, 2]+k^2/2)/n0.tilda
#   PPV.hat = S.tilda*p/(S.tilda*p+(1-C.tilda)*(1-p))
#   NPV.hat = C.tilda*(1-p)/((1-S.tilda)*p+C.tilda*(1-p))
#   return(list(PPV = PPV.hat, 
#               NPV = NPV.hat))
# }
source("CIpvBI_Thall.R")
library(runjags)
library(coda)
library(bdpv)
library(parallel)
library(ggplot2)
# dotR <- file.path(Sys.getenv("HOME"), ".R")
# if (!file.exists(dotR)) dir.create(dotR)
# M <- file.path(dotR, "Makevars")
# if (!file.exists(M)) file.create(M)
# cat("\nCXX14FLAGS=-O3 -march=native -mtune=native -fPIC",
#     "CXX14=g++", # or clang++ but you may need a version postfix
#     file = M, sep = "\n", append = TRUE)
# 
# cat("\nCXX14FLAGS=-O3 -march=native -mtune=native -fPIC",
#     "CXX14=g++-8", # or clang++ but you may need a version postfix
#      sep = "\n")
# cat("\nCXX14FLAGS=-O3 -march=native -mtune=native -fPIC",
#     "CXX14=g++", # or clang++ but you may need a version postfix
#     file = M, sep = "\n", append = TRUE)
cat("\nCXX14FLAGS=-O3 -march=native -mtune=native -fPIC",
    "CXX14=g++ -std=c++11", "CXX14FLAGS+= -std=c++11", "CXX14STD='-std=c++11'", # or clang++ but you may need a version postfix
    file = M, sep = "\n", append = TRUE)
# 
# remove.packages("StanHeaders")
# remove.packages("BH")
# scl enable devtoolset-8 -- bash
# export LD_LIBRARY_PATH=/home/xix66/local/lib:/usr/lib:/usr/local/lib64:/usr/lib64
```

## Overview 

The main goal of this simulation is to implement the method in @stamey2009bayesian, and compare the result with the log odds update in @thall2003hierarchical. The benchmark of the CI performance is the coverage of the CI. 

## Methods 

CI calculation methods: 

  * Logit transformed CI (or adjusted when the table contains 0) <!-- use the bdpv::BDtest -->
  * Bayesian CI with known prevalence, beta prior for Sensitivity (S) and Specificity (C) <!-- use the bdpv::CIpvBI -->
  * Bayesian CI with beta prior for prevalence, S and C <!-- use the bdpv::CIpvBII --> 
  * Bayesian CI with known prevalence, logit-normal prior for S and C. 

## Simulate data with different settings

```{r}
n1 = seq(20, 100, by = 20); #n0 = seq(20, 100, by = 20)
prev = c(0.005, 0.05, seq(0.1, 0.9, by = 0.2)) 
Se = seq(0.1, 0.9, by = 0.2)
Sp = seq(0.1, 0.9, by = 0.2)
params = expand.grid(n1 = n1, prev = prev, Se = Se, Sp = Sp, rep = seq_len(1000))
```

```{r, eval=FALSE}
time.start = Sys.time()
res = lapply(1:nrow(params), function(a){
  n1 = params$n1[a]
  n0 = params$n1[a]
  prev = params$prev[a]
  Se = params$Se[a]
  Sp = params$Sp[a]
  
  set.seed(params$rep)
  tab.2by2 = r.2by2(n1, n0, Se, Sp)
  
  logit.ppv = CombCIppv(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev, conf.level = 0.95, alternative = "two.sided")
  logit.npv = CombCInpv(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev, conf.level = 0.95, alternative = "two.sided")
  
  Bayes1 = CIpvBI(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev)
  Bayes2 = CIpvBII(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev, xpr = c(ceiling(500*prev), ceiling(500*(1-prev))))
  
  Bayes3 = CIpvBI_Thall(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev)
  
  one.row = params[a, ]
  one.row$PPV.truth = Se*prev/(Se*prev+(1-Sp)*(1-prev))
  one.row$NPV.truth = 1-Sp*(1-prev)/((1-Se)*prev+1-Sp*(1-prev))
  res.out = rbind.data.frame(cbind.data.frame(one.row, method = "logit", 
                                              PPV.est = logit.ppv$estimate, PPV.lower = logit.ppv$conf.int[1], PPV.upper = logit.ppv$conf.int[2], 
                                              NPV.est = logit.npv$estimate, NPV.lower = logit.npv$conf.int[1], NPV.upper = logit.npv$conf.int[2]), 
                             cbind.data.frame(one.row, method = "Bayes_beta_known_prev", 
                                              PPV.est = Bayes1$estimate["PPV"], PPV.lower = Bayes1$conf.int["PPV", 1], PPV.upper = Bayes1$conf.int["PPV", 2],
                                              NPV.est = Bayes1$estimate["NPV"], NPV.lower = Bayes1$conf.int["NPV", 1], NPV.upper = Bayes1$conf.int["NPV", 2]), 
                             cbind.data.frame(one.row, method = "Bayes_beta_unknown_prev", 
                                              PPV.est = Bayes2$estimate["PPV"], PPV.lower = Bayes2$conf.int["PPV", 1], PPV.upper = Bayes2$conf.int["PPV", 2],
                                              NPV.est = Bayes2$estimate["NPV"], NPV.lower = Bayes2$conf.int["NPV", 1], NPV.upper = Bayes2$conf.int["NPV", 2]), 
                             cbind.data.frame(one.row, method = "Bayes_logit_norm", 
                                              PPV.est = Bayes3$estimate["PPV"], PPV.lower = Bayes3$conf.int["PPV", 1], PPV.upper = Bayes3$conf.int["PPV", 2],
                                              NPV.est = Bayes3$estimate["NPV"], NPV.lower = Bayes3$conf.int["NPV", 1], NPV.upper = Bayes3$conf.int["NPV", 2]))
  res.out$PPV.cover = (res.out$PPV.truth>res.out$PPV.lower)&(res.out$PPV.truth<res.out$PPV.upper)
  res.out$PPV.CI.width = res.out$PPV.upper-res.out$PPV.lower
  res.out$NPV.cover = (res.out$NPV.truth>res.out$NPV.lower)&(res.out$NPV.truth<res.out$NPV.upper)
  res.out$NPV.CI.width = res.out$NPV.upper-res.out$NPV.lower
  print(paste0(a/nrow(params)))
  print(paste0("Time spent = ", Sys.time()-time.start))
  print(paste0("Time remain = ", (Sys.time()-time.start)/a*(nrow(params)-a)))
  
  return(res.out)
})
saveRDS(res, "simres_logit_normal.rds")
```

```{r}
#a test block
a = 1
  n1 = 50
  n0 = 50
  prev = 0.05
  Se = 0.8
  Sp = 0.8
  
  set.seed(1)
  tab.2by2 = r.2by2(n1, n0, Se, Sp)
  
  Bayes3 = CIpvBI_Thall(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev)
  Bayes3 = CIpvBI_Thall_stan(x0 = tab.2by2$Disease0, x1 = tab.2by2$Disease1, prev)
  
```


```{r}
#summary for the result 
res.tab = do.call(rbind.data.frame, res)


```

## A project plan

### Project 1

I think I should come up with a plan for the CI estimating. There are many ways we can borrow from binomial p CI coverage. The key is find reasonable ways of estimation and then do benchmark. This could be achieved by literature searching. 

### Project 2
